INGRID: Creating Languages in MPS from ANTLR Grammars

### 2016-10-27 chapters/language_definition.tex
shortcuts - in progress

@@

The key idea of this approach is to identify rules and nodes that are at the end of the (derivation, inheritance) chain, and offer them directly to the user through the auto-completion menu.
We call such \emph{end rules} and \emph{end nodes}, respectively, because they cannot transparently break into more rules/nodes.

>>>>

The key idea of this approach is to avoid all the intermediary layers (nodes) in the syntax tree by considering just the leaf nodes.

% TODO put here the example from below

When given a particular AST node $n$ (or a rule of the grammar) as input, the parser tree (AST) built in the earlier phases is systematically traversed in order to identify each AST node that may appear at the end of a derivation chain from the input node $n$.

@@

The key idea of this approach is to identify rules and nodes that are at the end of the (derivation, inheritance) chain

We call such \emph{end rules} and \emph{end nodes}, respectively, because they cannot transparently break into more rules/nodes.

End nodes and rules are then directly offered to the user through the auto-completion menu.
